Package Tests

### 2020-08-14 r-package/tests_marcus/rjava_tests.Rmd
Added @export tag to matrix calculation functions

origins_df <- read_csv(paste0(data_path, "poa_hexgrid.csv"))  %>% sample_n(20)
destinations_df <- read_csv(paste0(data_path, "poa_hexgrid.csv")) %>% sample_n(100)

travel_times <- r5_travel_time_matrix(r5r_core, origins = origins_df, destinations = destinations_df, 
                                      direct_modes = "WALK", transit_modes = "BUS", 
                                      trip_date, departure_time, street_time, trip_time)

>>>>

origins_df <- read_csv(paste0(data_path, "poa_hexgrid.csv"))  %>% sample_n(100)
destinations_df <- read_csv(paste0(data_path, "poa_hexgrid.csv")) %>% sample_n(100)

travel_times <- r5_travel_time_matrix(r5r_core, origins = origins_df, destinations = destinations_df, 
                                      direct_modes = c("WALK"), transit_modes = "", 
                                      trip_date, departure_time, street_time, trip_time)
